

---
Batting Statistics Visualization
===

In this document, I will explain the steps taken to create a graphical visualizaiton of batting statistics from 2010-2015.


###Graph 1

The first graph is a visualization of all the professional players from the Houston Astros and the Texas Rangers from 2010-2015. The graph compares the intentional walks to the total home runs by players on each Texas team.

```{r}
source("../02 Data Wrangling/IBB vs HR.R", echo = TRUE)
```



###Graph 2

The second graph is a visualization of all the professional players from 2010-2015. This graph compares the number of bases stolen to the times players were caught stealing by the the league each player is in.

```{r}
source("../02 Data Wrangling/Stolen Bases vs Caught Stealing.R", echo = TRUE)
```


###Graph 3

The third graph is a visualization of all the professional players from 2010-2015. This graph compares the strikeouts versus the hits by players for each year.

```{r}
source("../02 Data Wrangling/Strikeouts vs Hits.R", echo = TRUE)
```
